Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-21 src/ms.tex
appendix edits

\edit1{We also note that the short-period pile-up is not as prominent in the \lamostsan sample, compared to the \lamostmcq sample (see the rightmost panels of Figure~\ref{fig:xmatch}). The differences between the \citet{McQuillan2014} and \citet{Santos2021} catalogs may provide an explanation for this observation: the latter catalog contains a much larger number of detections at longer rotation periods. The higher sensitivity to more slowly rotating stars within the \citet{Santos2021} may then make the short-period pile-up appear weaker relative to the long-period pile-up, as expected since open cluster obsbervations suggest that the short-period pile-up can not be a long-lived feature.}

>>>>

\edit1{We also note that the short-period pile-up is not as prominent in the \lamostsan sample, compared to the \lamostmcq sample (see the rightmost panels of Figure~\ref{fig:xmatch}). The differences between the \citet{McQuillan2014} and \citet{Santos2021} catalogs may provide an explanation for this observation. The latter catalog contains a much larger number of detections at longer rotation periods, and the higher sensitivity to more slowly rotating stars within the \citet{Santos2021} may then make the short-period pile-up appear weaker relative to the long-period pile-up. This is as expected since open cluster obsbervations suggest that the short-period pile-up can not be a long-lived feature, while the long-period pile-up appears to be much longer lived. Consequently, the \citet{Santos2021} catalog may more accurately reflect the relative strengths of these two features.}
